Supplementary information

### 2021-09-27 _targets.Rmd
add toy scoring workflow

---
title: "Target Markdown"
output: html_document
---

@@

Target Markdown is a powerful R Markdown interface for reproducible analysis pipelines, and the chapter at https://books.ropensci.org/targets/markdown.html walks through it in detail. This R Markdown report the example from the chapter. Try it out in both interactive and non-interactive modes, either by running the code chunks in different ways or setting the `tar_interactive` chunk option.

# Packages

The example requires several R packages, and `targets` must be version 0.5.0.9000 or above.

```{r, eval = FALSE}
install.packages(c("biglm", "dplyr", "ggplot2", "readr", "targets", "tidyr"))
```

@@

If you are using old versions of `targets` (<= 0.7.0) and/or `knitr` (<= 1.33), you will need to load the `targets` package in the R Markdown document in order for Target Markdown code chunks to work.

```{r}
library(targets)
```

Near the top of the document, you may also wish to remove the `_targets_r` directory previously written by non-interactive runs of the report. Otherwise, your pipeline may contain superfluous targets.

```{r}
library(targets)
tar_unscript()
```

# Globals

We first define some global options/functions common to all targets. The function below plots a histogram of ozone concentrations, and our histogram target will need it.

```{targets example-globals, tar_globals = TRUE}
options(tidyverse.quiet = TRUE)
tar_option_set(packages = c("biglm", "dplyr", "ggplot2", "readr", "tidyr"))
create_plot <- function(data) {
  ggplot(data) +
    geom_histogram(aes(x = Ozone), bins = 12) +
    theme_gray(24)
}
```

# Targets

Our first target borrows the `airquality` dataset built into base R.

```{targets raw-data}
tar_target(raw_data, airquality)
```

Our next targets preprocess the data, make a histogram, and fit a model.

```{targets downstream-targets}
list(
  tar_target(data, raw_data %>% filter(!is.na(Ozone))),
  tar_target(hist, create_plot(data))
)
```

Set the `tar_simple` chunk option to `TRUE` to define a single target with the command in the code chunk. The chunk below only contains `biglm(Ozone ~ Wind + Temp, data)` in the source, but because `tar_simple` is `TRUE`, it is shorthand for `tar_target(name = fit, command = biglm(Ozone ~ Wind + Temp, data))`. All other arguments to `tar_target()` are set to their default values (configurable with `tar_option_set()`).

@@

If you ran all the `{targets}` chunks in non-interactive mode, then your R scripts are set up to run the pipeline.

```{r}
tar_make()
```

# Output

You can retrieve results from the `_targets/` data store using `tar_read()` or `tar_load()`.

```{r}
tar_read(hist)
```

The `targets` dependency graph helps your readers understand the steps of your pipeline at a high level.

```{r}
tar_visnetwork()
```

At this point, you can go back and run `{targets}` chunks in interactive mode without interfering with the code or data of the non-interactive pipeline.

>>>>

---
title: "Supplementary information"
output: html_document
---

@@

@@

Set up the workflow pipeline and options. We first load the `targets` package and remove the potentially outdated workflow.

```{r}
library(targets)
library(tibble)
library(tidyr)
library(dplyr)
library(scoringutils)
library(ggplot2)
library(purrr)
library(here)
tar_unscript()
```

We now define shared global options across our workflow and load R functions from the `R` folder.

```{targets globals, tar_globals = TRUE}
options(tidyverse.quiet = TRUE)
library(purrr)
library(here)
functions <- list.files(here("R"), full.names = TRUE)
walk(functions, source)
tar_option_set(
  packages = c("tibble", "tidyr", "dplyr", "scoringutils", "ggplot2", "purrr")
)
```

# Toy example

An exponential process with a certain rate r; and 3 forecasting models: one that thinks it’s exponential with rate r-a , one that thinks it’s exponential with rate r+a and one that thinks it’s linear; and compare scoring on linear and log scale for increasing horizons.

```{targets toy_scenarios, tar_simple = TRUE}
expand_grid(
  init = c(100),
  r = c(0, 0.01, 0.1, -0.01, -0.1),
  r_error = c(0, 0.01, 0.05, 0.1, -0.01, -0.05, -0.1),
  additive_error = c(0, 1, 10, -1, -10)
) |> 
  mutate(id = 1:n())
```

```{targets toy_simulations, tar_simple = TRUE}
toy_scenarios |>
  rowwise() |>
  mutate(y = list(
    simulate_exp_poisson(init = init, time = 10, growth = r + r_error,
                         additive_error = additive_error, sims = 1000)
    )
  ) |>
  unnest(cols = c(y))
```

```{targets toy_truth, tar_simple = TRUE}
toy_simulations |>
  filter(r_error == 0, additive_error == 0, sim == 1) |>
  select(init, r, time, true_value = obs)
```

```{targets toy_forecasts, tar_simple = TRUE}
toy_simulations |>
  filter(!(r_error == 0 & additive_error == 0)) |>
  select(init, r, r_error, additive_error, time, sample = sim,
         prediction = obs) |>
  left_join(toy_truth, by = c("init", "r", "time"))
```

```{targets, toy_scores, tar_simple = TRUE}
toy_forecasts |>
  eval_forecasts(
    summarise_by = c("init", "r", "r_error", "additive_error"),
    metrics = c("crps")
  )
```

```{targets, toy_log_scores, tar_simple = TRUE}
toy_forecasts |>
  mutate(across(.cols = c("true_value", "prediction"), ~ log(.x))) |>
  eval_forecasts(
    summarise_by = c("init", "r", "r_error", "additive_error"),
    metrics = c("crps")
  )
```

@@

If all`{targets}` were run in non-interactive mode, then the pipeline is ready to run using the following,

```{r, eval = FALSE}
tar_make()
```

The complete pipeline can be visualised using,

```{r, eval = FALSE}
tar_visnetwork()
```
